### 2023-04-14 manuscript.tex
Place holder for 'ethics statement' [ci skip]
This build is based on
https://github.com/habi/EAWAG-manuscript/commit/460de55a8763ac5b835ecc6e7c55af3d489d4d93.

This commit was created by the following CI build and job:
https://github.com/habi/EAWAG-manuscript/commit/460de55a8763ac5b835ecc6e7c55af3d489d4d93/checks
https://github.com/habi/EAWAG-manuscript/actions/runs/4700963193

\emph{A preprint of this manuscript is available at bioRχiv with the \href{https://doi.org/10.1101/2023.03.30.534917}{doi:10.1101/2023.03.30.534917}.}
\emph{We submitted \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.0}{\texttt{v1.0}} of the manuscript to \href{https://www.reviewcommons.org/}{Review Commons}, aiming for \href{https://journals.plos.org/plosone/}{PLOS ONE}.}
\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/v1.0...3e8bdc73d50e9e237a11c9c271a26468f5a9f151}{has been updated} since submission.}

This manuscript
(\href{https://habi.github.io/EAWAG-manuscript/v/3e8bdc73d50e9e237a11c9c271a26468f5a9f151/}{permalink})
was automatically generated
from \href{https://github.com/habi/EAWAG-manuscript/tree/3e8bdc73d50e9e237a11c9c271a26468f5a9f151}{habi/EAWAG-manuscript@3e8bdc7}
on April 14, 2023.

@@

>>>>

\emph{A preprint of this manuscript is available at bioRχiv with the \href{https://doi.org/10.1101/2023.03.30.534917}{doi:10.1101/2023.03.30.534917}.}
\emph{We submitted \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.0}{\texttt{v1.0}} of the manuscript to \href{https://www.reviewcommons.org/}{Review Commons}, aiming for \href{https://journals.plos.org/plosone/}{PLOS ONE}.}
\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/v1.0...460de55a8763ac5b835ecc6e7c55af3d489d4d93}{has been updated} since submission.}

This manuscript
(\href{https://habi.github.io/EAWAG-manuscript/v/460de55a8763ac5b835ecc6e7c55af3d489d4d93/}{permalink})
was automatically generated
from \href{https://github.com/habi/EAWAG-manuscript/tree/460de55a8763ac5b835ecc6e7c55af3d489d4d93}{habi/EAWAG-manuscript@460de55}
on April 14, 2023.

@@

\hypertarget{ethics-statement}{%
\subsubsection{Ethics statement}\label{ethics-statement}}
